\title{Project: Applying security and usability in practice}
\author{Daniel Bosk}

\maketitle

\mode*

%\begin{abstract}
%  \input{abstract.tex}
%\end{abstract}

\section{Introduction}%
\label{sec:intro}

\input{abstract.tex}


\section{Assignment}%
\label{sec:work}

Improve a current product or invent a new one.
The focus should be to use or incorporate research results from the area of 
information security.
\Eg it could be to improve privacy properties for streaming 
services~\cite[\eg][]{anonpass} or
improve usability and security for payment systems.

First look at the current usability and security in the area.
Look for published research that improves the situation.
Suggest improvements and methods to evaluate these.

You should summarize your work in a report.
First summarize how you performed your evaluation, what its results are.
Then summarize your suggestions with motivations why these improve the 
situation.

Based on your report, make a presentation that will be a research-founded 
\enquote{sales pitch} to your security-aware classmates.


\section{Examination}%
\label{sec:exam}

The report must be handed-in in the course platform in PDF or PostScript 
format, no other formats are accepted.
You can find the timeslots for presentations in the course schedule.

The report will be graded according to the following grading criteria:
\begin{description}
  \item[Grade E] You fulfil all the \acp{ILO} above.
    You should have identified a relevant problem, and given a solution to it.
    It must be a viable solution, however gaps and mistakes are allowed, if 
    they don't render your solution unusable.

  \item[Grade C] You fulfil the criteria for E.
    Additionally, your evaluations and designs are \emph{good} with \emph{some 
      base} in theory and, where applicable, the research literature.
    Gaps and errors are allowed if they only render your solution less optimal.

  \item[Grade A] You fulfil the criteria for C.
    However, your evaluations and designs must be \emph{extensive} and 
    \emph{well-founded} in theory and, where applicable, the research 
    literature.
    Gaps and errors are not allowed in the solution unless they have been 
    properly addressed and you have given a suggestion on an approach to how to 
    start solve the issue.
\end{description}
The grades B and D are intermediary grades.
When assessing the multi-dimensional domain of your work, we will try to make 
as fair a projection as possible onto this linear scale.

The assignment may be done in groups of three to four people.
However, if the proposed project is of proper size you may be excused from this 
limit.
Talk to the tutor and motivate why you need to deviate from the group size.


\printbibliography
